Gas Fractions of Galaxies Across Simulations

### 2018-07-12 mnras_template.tex
Update on Overleaf.

\section{Simulations and Data Selection}
\begin{table*}
\centering
\caption{Caption}
\label{table:simulations}
  \begin{tabular}{l c c c c c c c}
  \hline
  Simulation & Baryon Res. (10$^6$ M$_{\odot}$) & DM Res. (10$^6$ M$_{\odot}$) & Vol. (x cMpc)$^3$ & $\epsilon$ (ckpc) & Gas Def. & Pressure Floor & Ref. \\
  \hline 
  Illustris  & 1.26 ($\Delta x$ = 48 cpc) & 6.26 & 106.5 & 0.71 / 1.42 & &  & \citep{Vogelsberger2014} \\
  %Illustris-TNG & & & \\
  MUFASA & 18.2 & 96 & 50 & 0.5 & & & \citep{Dave2016} \\
  EAGLE  & 1.81 &  9.70  & 100 & 0.70 (pkpc) & &  & \citep{Schaye2015,Crain2015} \\
  Brooks & & &  & & & & \\
  SC-SAM & -  & - & & - & - & & \citep{Somerville2012,Porter2014}\\
  \hline
  \end{tabular}

@@

The works considered here treat the sub-grid physics required to model individual gas components (e.g. H, He, H$_2$) and their ionization states somewhat differently. Each of the big-box simulations lack the resolution and physics needed to self-consistently model each ionization state. Rather, these are computed through some approximation either live during the simulation (EAGLE) or via post-processing (MUFASA). Though each of these methods are similar, they likely do not produce identical results; characterizing the variation in galaxy gas properties caused by different ionization models is beyond the scope of this work. If H$_2$ is followed, we compute the gas mass of each galaxy as the total neutral hydrogen mass, or M$_{\rm gas}$ = M$_{\rm H_2}$ + M$_{\rm \ion{H}{i}}$ (EAGLE, MUFASA,Brooks), otherwise we take M$_{\rm gas}$ = M$_{\rm \ion{H}{i}}$ if H$_2$ is not tracked (Illustris, SC-SAM). This is a more faithful comparison than taking M$_{\rm \ion{H}{i}}$ alone, as the H$_2$ content in these works is derived directly from the \ion{H}{i} content. We define gas fraction here as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm HI}}{M_{\rm HI} + M_{*}},
\end{equation}
though we note some authors consider instead the the ratio $M_{\ion{H}{i}} / M_{*}$.

@@

\subsection{Brooks zooms}
\label{sec:Brooks method}
{\it ask Alyson for text}

@@

\subsection{Stellar Mass Halo Mass Relationship}
\label{sec:results:SMHM}
{\bf missing data at the moment}
{\it Discuss SMHM relationship across the works. Discuss how their similarities / differences may affect how to interpret rest of paper (though they should probably be similar?).  Possibly also shade with median gas fraction... this should be similar (maybe) across works}

@@

\subsection{Gas fraction vs stellar mass}
\label{sec:results:fg Mstar}

@@

By nature of plotting gas fraction in logsapce, these diagrams exclude any galaxies with no gas content. To help clarify these populations across datasets we plot the median gas fraction (including galaxies with f$_{\rm gas}$ = 0) as a function of stellar mass in the top panel of Figure~\ref{fig:linear fgas mstar}, including the Brooks zoom-in simulations. The shaded regions in each encompass the innerquartile range of each distribution; in stellar mass bins with less than 10 galaxies we plot points instead of the median curve. In the bottom panel, we show the fraction of galaxies in stellar mass bins that are devoid of gas for each data source. The same trends observed in Figure~\ref{fig:fgas mstar 2D} are clear here as well: Illustris galaxies are tightly distributed with high gas fractions at fixed stellar mass, as compared to EAGLE, MUFASA, and the SC-SAM which have comparable gas fractions and wider distributions. At low stellar mass, the SC-SAM approaches unity, unlike MUFASA and EAGLE.

@@

>>>>

\section{Simulations and Data Selection}
\begin{table*}
\centering
\caption{Caption}
\label{table:simulations}
  \begin{tabular}{l c c c c c c c}
  \hline
  Simulation & Baryon Res. (10$^6$ M$_{\odot}$) & DM Res. (10$^6$ M$_{\odot}$) & Vol. (x cMpc)$^3$ & $\epsilon$ (ckpc) & Gas Def. & Pressure Floor & Ref. \\
  \hline 
  Illustris  & 1.26 ($\Delta x$ = 48 cpc) & 6.26 & 106.5 & 0.71 / 1.42 & &  & \citep{Vogelsberger2014} \\
  %Illustris-TNG & & & \\
  MUFASA & 18.2 & 96 & 50 & 0.5 & & & \citep{Dave2016} \\
  EAGLE  & 1.81 &  9.70  & 100 & 0.70 (pkpc) & &  & \citep{Schaye2015,Crain2015} \\
  SC-SAM & -  & - & & - & - & & \citep{Somerville2012,Porter2014}\\
  \hline
  \end{tabular}

@@

The works considered here treat the sub-grid physics required to model individual gas components (e.g. H, He, H$_2$) and their ionization states somewhat differently. Each of the big-box simulations lack the resolution and physics needed to self-consistently model each ionization state. Rather, these are computed through some approximation either live during the simulation (EAGLE) or via post-processing (MUFASA). Though each of these methods are similar, they likely do not produce identical results; characterizing the variation in galaxy gas properties caused by different ionization models is beyond the scope of this work. If H$_2$ is followed, we compute the gas mass of each galaxy as the total neutral hydrogen mass, or M$_{\rm gas}$ = M$_{\rm H_2}$ + M$_{\rm \ion{H}{i}}$ (EAGLE, MUFASA), otherwise we take M$_{\rm gas}$ = M$_{\rm \ion{H}{i}}$ if H$_2$ is not tracked (Illustris, SC-SAM). This is a more faithful comparison than taking M$_{\rm \ion{H}{i}}$ alone, as the H$_2$ content in these works is derived directly from the \ion{H}{i} content. We define gas fraction here as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm HI}}{M_{\rm HI} + M_{*}},
\end{equation}
though we note some authors consider instead the the ratio $M_{\ion{H}{i}} / M_{*}$.

@@

@@

\subsection{Stellar Mass Halo Mass Relationship}
\label{sec:results:SMHM}
{\it Discuss SMHM relationship across data with references to original publications. Main story: Stellar properties of galaxies are similar (this is one example). Physics that generates these similar properties is very different. Leads into how this may affect related but un-tuned properties (i.e. gas).}

@@

\subsection{Gas Fraction and Gas Mass vs stellar mass}
\label{sec:results:fg Mstar}

@@

By nature of plotting gas fraction in logsapce, these diagrams exclude any galaxies with no gas content. To help clarify these populations across datasets we plot the median gas fraction (including galaxies with f$_{\rm gas}$ = 0) as a function of stellar mass in the top panel of Figure~\ref{fig:linear fgas mstar}. The shaded regions in each encompass the innerquartile range of each distribution; in stellar mass bins with less than 10 galaxies we plot points instead of the median curve. In the bottom panel, we show the fraction of galaxies in stellar mass bins that are devoid of gas for each data source. The same trends observed in Figure~\ref{fig:fgas mstar 2D} are clear here as well: Illustris galaxies are tightly distributed with high gas fractions at fixed stellar mass, as compared to EAGLE, MUFASA, and the SC-SAM which have comparable gas fractions and wider distributions. At low stellar mass, the SC-SAM approaches unity, unlike MUFASA and EAGLE.

@@

\textit{ Establish definition of SFMS from Paper I. Discuss Figure~\ref{fig:SFMS fgas}. 
\begin{enumerate}
\item Significant variation among simulations as to where (relative to SFMS) galaxies are gas-rich and gas-poor.
\item SFMS slope is somewhat correlated with EAGLE f$_{\rm gas}$ = 0.5 line. Is this significant? Should they be related?
\item SCSAM galaxies at low stellar masses are gas rich above and below SFMS.
\end{enumerate}
}

\subsubsection{Distance from the main sequence and gas properties}
\label{sec:distance SFMS}
